Reparametrization of COM-Poisson Regression Models with Applications in the Analysis of Experimental Data

### 2018-01-28 article.Rnw
Improve the concluding remarks section

In this paper, we presented a novel parametrization of the COM-Poisson
distribution and the associated regression model. The novel
parametrization was based on a simple asymptotic approximation for the
expectation and variance of the COM-Poisson distribution. The main
advantage of the proposed reparametrization is the simple interpretation
of the regression coefficients in terms of the expectation of the
response variable as usual in the generalized linear models
context. Thus, it is possible to compare the results of the COM-Poisson
model with the ones from standard approaches as the Poisson and
quasi-Poisson regression models. Furthermore, in the novel
parametrization the COM-Poisson distribution is indexed by the
expectation $\mu$ and an extra dispersion parameter $\phi$ which our
data analysis suggest to be orthogonal.

We evaluated the accuracy of the asymptotic approximations for the
expectation and variance of the COM-Poisson distribution by considering
quadratic approximation errors.  The results showed that the
approximations are accurate for a large part of the parameter space,
which in turn support our reparametrization.  We carried out a
simulation study to assess the properties of the reparametrized
COM-Poisson model to deal with different levels of dispersion as well as
the properties of the maximum likelihood estimators. The results of our
simulation study suggested that the maximum likelihood estimators of the
regression and dispersion parameters are unbiased and consistent.  The
empirical coverage rates of the confidence intervals computed based on
the asymptotic distribution of the maximum likelihood estimators are
close to the nominal level for sample size greater than $100$.  The
worst scenario is when we have small sample sizes and strong
overdispersed counts.  In general, we recommend the use of the
asymptotic confidence intervals for computational simplicity.

>>>>

In this paper, we presented and characterized a novel parametrization of
the COM-Poisson distribution and the associated regression model. The
novel parametrization was based on a simple asymptotic approximation for
the expectation and variance of the COM-Poisson distribution. The main
advantage of the proposed reparametrization is the simple interpretation
of the regression coefficients in terms of the expectation of the
response variable as usual in the generalized linear models
context. Thus, it is possible to compare the results of the COM-Poisson
model with the ones from standard approaches as the Poisson and
quasi-Poisson regression models. Furthermore, in the novel
parametrization the COM-Poisson distribution is indexed by the
expectation $\mu$ and an extra dispersion parameter $\phi$ which our
data analysis suggest being orthogonal. This is similar to
\Citeauthor{Huang2017}'s (\citeyear{Huang2017}) parametrization but is
simpler, because the $\mu$ is obtained from simple algebra.

We evaluated the accuracy of the asymptotic approximations for the
expectation and variance of the COM-Poisson distribution by considering
quadratic approximation errors.  The results showed that the
approximations are accurate for a large part of the parameter space,
which in turn support our reparametrization. Moreover, we discuss the
properties and flexibility of the distribution to deal with count data
although dispersion, zero-inflation and heavy-tail indexes. We carried
out a simulation study to assess the properties of the reparametrized
COM-Poisson model to deal with different levels of dispersion as well as
the properties of the maximum likelihood estimators. The results of our
simulation study suggested that the maximum likelihood estimators of the
regression and dispersion parameters are unbiased and consistent.  The
empirical coverage rates of the confidence intervals computed based on
the asymptotic distribution of the maximum likelihood estimators are
close to the nominal level for sample size greater than $100$.  The
worst scenario is when we have small sample sizes and strong
overdispersed counts.  In general, we recommend the use of the
asymptotic confidence intervals for computational simplicity.
